A continuous urbanization index to assess phylogenetic adaptations in urban bird living

### 2018-05-15 ms.Rmd
a lot of reworking the discussion!

# DISCUSSION

Niche breadth, as measured by different types of generalism, was significantly associated with our urbanization index. This result was robust across non-phylogenetic and phylogenetic models, model averaging approaches, and across phylogenetic uncertainty. Conversely, specialized feeding strategies were negatively associated with urbanization: granivorous and insectivorous specialists were much less likely to be found in urban environments. These results suggest that urbanization is, in general, excluding most specialist species.  SOMETHING ABOUT IMPLICATIONS FOR CONSERVATION / FRAGMENTATION.

@@

Certian aspects of the trait-urbanization relationship appear to be consistent across the globe. CHANGE PHRASING BELOW HERE: The relationship with annual fecundity and urbanization in birds is consistent with work in Europe  [@croci2008does; @moller2009successful]. The that urbanization appears to select against insectivorous species [@chace2006urban; @evans2011makes]. While others have found that urbanization supports granivorous species [@chace2006urban; @kark2007living; @evans2011makes], we found the opposite trend, but this could be a result of relatively little supplementary feeding in Australian cities [cf., @fuller2008garden]. We did not find any strong support for our hypotheses on different nesting types, but we did find that in general, species which tended to be more social were at an advantage to city living, confirming previous studies [@coleman1994neophobia; @jokimaki1998distribution; @kark2007living].

Clearly, many traits have been used to identify a species' adaptability with urban-living (e.g., Appendix 1), but often times results differ among studies. Fully understanding the suite of specific species' traits which are associated with urban birds allows for a better understanding of how to best preserve and maintain avian biodiversity in urban areas [@evans2011makes]. As previously noted, a major shortcoming of previous studies has been the focus on discrete classifications of species based on their responses to urbanization. Our models assessed the applicability of traits in relation to one another (i.e., we did not run separate models or statistical tests for each specific trait as previously done). The aforementioned differences in our results compared with others is likely due to increased sample size, as well as our use of a continuous measure of urbanization. Our results suggest that urbanization selects against specialist species [@sorace2009distribution], granivores, and insectivores. As such, future urban development aimed at increasing avian diversity should focus on maintaining a high diversity of habitat [@melles2003urban] both for foraging [@shochat2004linking], and nesting [@fernandez2001habitat]. A species-specific approach to assess particular resources necessary for specialist species may be necessary [@fernandez2004spatial]. Lastly, a focal point should be on increasing insect abundance and diversity in urban environments [@baldock2015uk], which will in turn increase the presence of insectivorous bird species in urban environments.

Global broad-scale empirical datasets are rapidly expanding our knowledge of urbanization impacts on birds [e.g., @aronson2014global; @aronson2016hierarchical; @gutierrez2018citizen], in large part due to the growing use of citizen science data [@silvertown2009new] in combination with advances in remote sensing technology [@gorelick2017google]. We used a novel approach, over a broad spatial and temporal scale, to quantify an urbanization index in birds. We did not explicitly account for changes throughout the annual cycle in a species' association with urban areas [e.g., @la2014role; @lepczyk2017global; @katuwaleffect], but migratory status was considered as a predictor. We highlight that future studies, especially within migrant-dominated landscapes (e.g., Europe, North America), should account for changes in a species' response to urbanization throughout the full-annual cycle [@hostetler2015full; @marra2015call]. Further, future studies should look to expand this analysis outside the scope of Australia, and also investigate whether these patterns hold true at multiple spatial scales [@suarez2018scale] (i.e., does city size affect the patterns found here; [@sol2017urbanisation; @batary2018non]).

Ultimately, we provide the largest study to date using a continuous urbanization metric in order to assess biological and ecological traits which predict a species' adaptability to urban environments. In doing so, we highlight the applicability of broad-scale empirical data to assess species' traits which predict presence and adaptability in urban environments. Our results suggest that generalist species, with large relative brain size, are better prepared to forage and survive in the ecologically novel aspects of urban environments [@shochat2006patterns]. Australia is a relatively young country with rapid urbanization currently underway [@coffee2016visualising] and fully understanding how birds respond to urban development is critical to inform future management. Urban avian biodiversity could be increased by improving the suitability of foraging for granivores and insectivores, especially important given the recent noted collapse of insects in other parts of the world [@hallmann2017more]. Furthermore, future studies should focus on broad-scale data to form generalizable patterns which rely on continuous measures for improved predictive performance.

>>>>

# DISCUSSION
Niche breadth, as measured by different types of generalism, was significantly associated with urbanization in our analysis. This result was robust across non-phylogenetic and phylogenetic models, model averaging approaches, and across phylogenetic uncertainty. Conversely, specialized feeding strategies were negatively associated with urbanization: granivorous and insectivorous specialists were much less likely to be found in urban environments. These results suggest that urbanization is, in general, excluding specialist species [@sorace2009distribution]. As such, future urban development aimed at increasing avian diversity in urban areas should focus on maintaining a high diversity of habitat [@melles2003urban] both for foraging [@shochat2004linking], and nesting [@fernandez2001habitat], with a focus on intact vegetation [@sushinsky2013should] connected by corridors [@litteral2017role]. A species-specific approach to assess particular resources necessary for specialist species may be necessary [@fernandez2004spatial]. Lastly, a focal point should be on increasing insect abundance and diversity in urban environments [@baldock2015uk], which will in turn increase the presence of insectivorous bird species in urban environments.

@@

Certian aspects of the trait-urbanization relationship appear to be consistent, and thus generalizable, across the globe. For instance, our finding of the relative importance of annual fecundity is consistent with work in Europe [@croci2008does; @moller2009successful]. Urbanization appears to generally select against insectivorous species [@chace2006urban; @evans2011makes]. Although we did not find any strong support for our hypotheses on different nesting types, we did find that in general species which tended to be more social were closely associated with urbanization, consistent with other findings [@coleman1994neophobia; @jokimaki1998distribution; @kark2007living]. While these patterns may be generalizable, we also found patterns in our analysis which seem to contrast the global norm. For example, we found that urbanization selects against granivorous species, contrasting the general trend [@chace2006urban; @kark2007living; @evans2011makes], but this could be a result of relatively little supplementary feeding in Australian cities [cf., @fuller2008garden].

As illustrated (above and in Appendix 1), many traits have been used to identify a species' adaptability to urban environments, but results have frequently differed among studies. As previously noted, a major shortcoming of previous studies has been the focus on discrete classifications of species based on their responses to urbanization. Our models assessed the applicability of traits in relation to one another (i.e., we did not run separate models or statistical tests for each specific trait as previously done). The aforementioned differences in our results compared with others is likely due to increased sample size, as well as our use of a continuous measure of urbanization. This analysis was made possible through the use of global broad-scale empirical datasets, which are rapidly expanding our knowledge of urbanization impacts on birds [e.g., @aronson2014global; @aronson2016hierarchical; @gutierrez2018citizen]. This is largely due to the growing use of citizen science data [@silvertown2009new] in combination with advances in remote sensing technology [@gorelick2017google]. We used a novel approach, over a broad spatial and temporal scale, to quantify an urbanization index in birds. We did not explicitly account for changes throughout the annual cycle in a species' association with urban areas [e.g., @la2014role; @lepczyk2017global; @katuwaleffect], but migratory status was considered as a predictor. We highlight that future studies, especially within migrant-dominated landscapes (e.g., Europe, North America), should account for changes in a species' response to urbanization throughout the full-annual cycle [@hostetler2015full; @marra2015call]. Further, future studies should look to expand this analysis outside the scope of Australia, and also investigate whether these patterns hold true at multiple spatial scales [@suarez2018scale] (i.e., does city size affect the patterns found here; [@sol2017urbanisation; @batary2018non]). Fully understanding the suite of specific species' traits which are associated with urban birds, and placing them in a theoretical landscape ecology context, will ultimately allow for a better understanding of how to best preserve and maintain avian biodiversity in urban areas [@evans2011makes].

We provide the largest study to date using a continuous urbanization metric in order to assess ecological and life history traits which are associated with a species' adaptability to urban environments. Our results suggest that generalist species, with large relative brain size, are better prepared to forage and survive in the ecologically novel aspects of urban environments [@shochat2006patterns]. This work should be extended to test whether our findings can accurately predict species which are commonly found in urban environments in other parts of the world, based on a known suite of traits associated with a given set of species. Australia is a relatively young country with rapid urbanization currently underway [@coffee2016visualising] and fully understanding how birds respond to urban development is critical to inform future management. Urban avian biodiversity could be increased by improving the suitability of foraging for granivores and insectivores, especially important given the recent noted collapse of insects in other parts of the world [@hallmann2017more]. Furthermore, future studies should focus on broad-scale data to form generalizable patterns which rely on continuous measures for improved predictive performance.
